NHF1 Deamination Anchored Excision Site Figure Generation

### 2022-06-22 R/NHF1DeaminationAnchoredExcisionSiteFigureGeneration.rmd
Fixing more mistakes...

```{r CPD_mismatch_anchored_purine_frequencies_filtered, fig.width = 11, fig.height = 9}
min3PrimeCutSiteDistance = 1
max3PrimeCutSiteDistance = 12

for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]], 
                                 title = paste(c("CPD", titleCaseFiltering,
                                                 "5' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                                 combineNucleotides = c("AG"), combinedNames = c("Purine"),
                                 posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                                 expansionOffset = expansionOffset,
                                 minReadLength = min3PrimeCutSiteDistance, maxReadLength = max3PrimeCutSiteDistance)
}
```

```{r CPD_mismatch_anchored_purine_frequencies_filtered_x2, fig.width = 5, fig.height = 9}
min3PrimeCutSiteDistance = 1
max3PrimeCutSiteDistance = 12

for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]][Timepoint == "1h"], 
                                 title = paste(c("CPD", titleCaseFiltering,
                                                 "5' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                                 combineNucleotides = c("AG"), combinedNames = c("Purine"),
                                 posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                                 expansionOffset = expansionOffset,
                                 minReadLength = min3PrimeCutSiteDistance, maxReadLength = max3PrimeCutSiteDistance)
}
```

>>>>

```{r CPD_mismatch_anchored_purine_frequencies_filtered, fig.width = 11, fig.height = 9}
min5PrimeCutSiteDistance = 13
max5PrimeCutSiteDistance = 25

for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq[[i]], 
                                 title = paste(c("CPD", titleCaseFiltering,
                                                 "3' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                                 combineNucleotides = c("AG"), combinedNames = c("Purine"),
                                 posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
                                 expansionOffset = expansionOffset,
                                 minReadLength = min5PrimeCutSiteDistance, maxReadLength = max5PrimeCutSiteDistance)
}
```

```{r CPD_mismatch_anchored_purine_frequencies_filtered_x2, fig.width = 5, fig.height = 9}
min5PrimeCutSiteDistance = 13
max5PrimeCutSiteDistance = 25

for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq[[i]][Timepoint == "1h"], 
                                 title = paste(c("CPD", titleCaseFiltering,
                                                 "3' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                                 combineNucleotides = c("AG"), combinedNames = c("Purine"),
                                 posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
                                 expansionOffset = expansionOffset,
                                 minReadLength = min5PrimeCutSiteDistance, maxReadLength = max5PrimeCutSiteDistance)
}
```
